COG-ED Manuscript

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
Aussage auf die Konstruktebene bezogen
Kommentar hinzugefügt
Zwicshenüberschrift eingefügt

A way to quantify the subjective cost of each n-back level has been developed by Westbrook et al. [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED). <!-- gibt es keine Möglichkeit, die Quelle automatisiert pasten zu lassen? Sonst müsste man an der Stelle auch zuerst alle drei Autoren nennen, oder?  -->
First, the participants complete the n-back levels to familiarize themselves with the task. <!-- habe es mal allgemeiner gehalten, da wir selbst auch keine sechs level haben  -->
Then, level one is compared with all following levels by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for level one. <!-- s. vorheriger Kommentar -->
If they choose the more difficult level, the reward for level one increases by 0.50\$, if the choose level one, it decreases by 0.50\$.
This is repeated five more times, with each adjustment of the level one reward being half as big as in the previous step, while the reward for the more difficult level remains fixed at 2\$.
The idea is to estimate subjective equivalence, i.e., both offers are equally preferred [@Westbrook2013]. 
The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of level one by the fixed 2\$ reward of the more difficult level.
Westbrook et al. [-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting by plotting the SVs and computing an area under the curve (AUC).
Younger participants had a larger AUC than older participants, i.e. they needed a lower monetary incentive for choosing the more difficult levels over level one.

The AUC in the study by Westbrook et al. [-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
However, the relation of NFC and SVs might be confounded with task performance itself, since subjective task values have been shown to depend on both the exerted effort [@Wang2017] and the expected performance [@Yee2021].
Findings on NFC and n-back performance are heterogenous.
On one hand individuals with higher NFC neither had better n-back performance [@Gaertner2021] nor better working memory [@Fleischhauer 2010; @Hill2013], on the other hand they showed greater attention allocation [@Enge2008] and brain flexibility [@He2019].
Nevertheless, a possible association of NFC and task performance might be secondary, since task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019].
But since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021], more research is needed to shed light on this issue.

>>>>

A way to quantify the subjective cost of each n-back level has been developed by Westbrook et al. [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED). <!-- gibt es keine Möglichkeit, die Quelle automatisiert pasten zu lassen? Sonst müsste man an der Stelle auch zuerst alle drei Autoren nennen, oder?  -->
First, the participants complete the n-back levels to familiarize themselves with the task. <!-- habe es mal allgemeiner gehalten, da wir selbst auch keine sechs level haben  -->
Then, level one is compared with all following levels by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for level one. <!-- s. vorheriger Kommentar -->
If they choose the more difficult level, the reward for level one increases by 0.50\$, if the choose level one, it decreases by 0.50\$.
This is repeated five more times, with each adjustment of the level one reward being half as big as in the previous step, while the reward for the more difficult level remains fixed at 2\$.
The idea is to estimate subjective equivalence, i.e., both offers are equally preferred [@Westbrook2013]. 
The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of level one by the fixed 2\$ reward of the more difficult level.
Westbrook et al. [-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting by plotting the SVs and computing an area under the curve (AUC). <!-- kann man das so sagen? Mit dem plotten? Vielleicht sollte man einfach nur sagen, die AUC wurde berechnet? -->
Younger participants showed lower effort discounting, i.e. they needed a lower monetary incentive for choosing the more difficult levels over level one. <!--Würde bei dieser Aussage eine Ebene höher gehen und dann also vom Effort Discounting sprechen -->

## Effort discounting and need for cognition 
<!-- denke eine Zwischenüberschrift könnte das noch etwas deutlicher unterteilen-->
The AUC in the study by Westbrook et al. [-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
However, the relation of NFC and SVs might be confounded with task performance itself, since subjective task values have been shown to depend on both the exerted effort [@Wang2017] and the expected performance [@Yee2021].
Findings on NFC and n-back performance are heterogenous.
On one hand individuals with higher NFC neither had better n-back performance [@Gaertner2021] nor better working memory [@Fleischhauer 2010; @Hill2013], on the other hand they showed greater attention allocation [@Enge2008] and brain flexibility [@He2019].
Nevertheless, a possible association of NFC and task performance might be secondary, since task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019].
But since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021], more research is needed to shed light on this issue.
